Spatial Analysis of Russian Law Firms Naming

### 2024-08-08 law-firms-names/Paper.Rmd
Minor fixes before submission, #5

```{r imports, cache=TRUE, include=FALSE}
library(here)
source(here("journal-article", "Script.R"))
```

@@

To address these challenges, a unified state registry of small and medium-sized businesses (SMB registry) may be used. The registry has been maintained since 2016 in accordance with Article 4.1 of the Federal Law of 24 July 2007 No. 209-FZ “On the development of small and medium-sized businesses in the Russian Federation”. All companies and individual entrepreneurs with a yearly revenue below 2 billion roubles and an average yearly number of employees below 250 are automatically included in the SMB registry, without any action being required on their part. The registry is fully downloadable at the FTS open data portal at no cost. Additionally, the portal provides a monthly record of updates made since the registry's inception. To sum it up, the SMB registry can be regarded as the most comprehensive free data source offering information on Russian business entities, both organizations and individuals.

@@

The Yandex Foundation Models cloud service is used to transform the firm names into text vectors, or embeddings. The “text-search-query” model is selected because its purpose, as stated in the documentation, is to vectorize short texts. Prior to vectorization, the firm names are preprocessed to remove indications of organizational form such as “limited liability company”. This is done because such indications are common to the majority of names and thus have little value. The results of the queries to the Yandex API are stored separately for reuse, given that API calls are paid and take time to be completed.

>>>>

```{r package-imports, include=FALSE}
library(dplyr)
library(ggplot2)
library(glue)
library(here)
library(readr)
library(readxl)
library(sf)
library(stringr)
library(tidyr)
library(units)
```

```{r data-imports, cache=TRUE, include=FALSE}
source(here("journal-article", "Script.R"))
```

@@

To address these challenges, a unified state registry of small and medium-sized businesses (SMB registry) may be used [@SMBRegistry2024]. The registry has been maintained since 2016 in accordance with Article 4.1 of the Federal Law of 24 July 2007 No. 209-FZ “On the development of small and medium-sized businesses in the Russian Federation”. All companies and individual entrepreneurs with a yearly revenue below 2 billion roubles and an average yearly number of employees below 250 are automatically included in the SMB registry, without any action being required on their part. The registry is fully downloadable at the FTS open data portal at no cost. Additionally, the portal provides a monthly record of updates made since the registry's inception. To sum it up, the SMB registry can be regarded as the most comprehensive free data source offering information on Russian business entities, both organizations and individuals.

@@

The Yandex Foundation Models cloud service [@Yandex2024] is used to transform the firm names into text vectors, or embeddings. The “text-search-query” model is selected because its purpose, as stated in the documentation, is to vectorize short texts. Prior to vectorization, the firm names are preprocessed to remove indications of organizational form such as “limited liability company”. This is done because such indications are common to the majority of names and thus have little value. The results of the queries to the Yandex API are stored separately for reuse, given that API calls are paid and take time to be completed.
